On-the-fly Algorithms for GKAT Equivalences \thanks{Identify applicable funding agency here. If none, delete this.}

### 2025-01-17 main.tex
make on-the-fly algorithm more similar to the symbolic one

\begin{algorithm}
    \caption{On-the-fly bisimulation algorithm}\label{alg:bisim}
    \begin{algorithmic}
        \Function{equiv}{$s ∈ S, u ∈ U$}
        \If {\Call{eq}{$s, u$}} {\Return true} \EndIf
        \If {\Call{knownDead\(_S\)}{$s$}} 
            \State\Return \Call{isDead\(_U\)}{$u$}
        \EndIf
        \If {\Call{knownDead\(_U\)}{$u$}} 
            \State\Return \Call{isDead\(_S\)}{$s$}
        \EndIf
        \For{\(α ∈ \At\)}{}{
            \Match{$δ_{S}(s, α), δ_{U}(u, α)$}
            \Case{\(\accept, \accept\)} {\Continue} \EndCase
            \Case{\(\reject, \reject\)} {\Continue} \EndCase
            \Case{\(\reject, (u', q)\)} 
                \State\Return \Call{isDead\(_U\)}{$u'$} 
            \EndCase
            \Case{\((s', p), \reject\)}
                \State\Return\Call{isDead\(_S\)}{$s'$}
            \EndCase
            \Case{\((s', p), (u', q)\)} {
                \If {\(p = q\)}
                    \State\Call{union}{$s, u$}
                    \State\Return \Call{equiv}{$s, t$} 
                \EndIf
                \If{\Call{isDead\(_S\)}{$s$} and \Call{isDead\(_U\)}{$u$}}
                    \State\Continue
                \EndIf
                \State\Return false
            } \EndCase
            \Default { \Return false } \EndDefault
            \EndMatch
        }\EndFor
        \State\Return true
        \EndFunction
    \end{algorithmic}
\end{algorithm}

@@

\begin{algorithm*}
    \caption{Symbolic On-the-fly Bisimulation Algorithm}\label{alg:symb-bisim}
    \begin{algorithmic}
        \Function{equiv}{$s ∈ S, u ∈ U$}
        \If {\Call{eq}{$s, u$}} {\Return true}
        \ElsIf {\Call{knownDead\(_S\)}{$s$}} {\Return \Call{isDead\(_U\)}{$u$}} 
        \ElsIf {\Call{knownDead\(_U\)}{$u$}} {\Return \Call{isDead\(_S\)}{$s$}} 
        \Else {}
        \Return {
            \Comment{conditions of ~\cref{thm:symb-recursive-construction}}
            \\\vspace{5px}
            \(\qquad
            \begin{aligned}
                & ⋁ ϵ̂_S(s) ≡ ⋁ ϵ̂_U(u) \mathrel{\&\!\&} \\  
                & ∀ (b, s', p) ∈ δ̂_S(s), (c, u', q) ∈ δ̂_U(u), (b ∧ c) ≢ 0 ⟹ 
                \begin{cases}
                    \text{\Call{isDead$_S$}{$s$}} ∧ \text{\Call{isDead$_U$}{$u$}} & \text{if \(p ≠ q\)} \\
                    \text{\Call{Union}{$s$, $u$}}; \text{\Call{Equiv}{$s', u'$}} & \text{if \(p = q\)}
                \end{cases} \mathrel{\&\!\&}\\
                & ∀ (b, s', p) ∈ δ̂_S(s), c ∈ ρ̂_U(u), (b ∧ c) ≢ 0 ⟹ \text{\Call{isDead$_S$}{$s'$}} \mathrel{\&\!\&}\\
                & ∀ b ∈ ρ̂_S(s), (c, u', q) ∈ δ̂_U(u), (b ∧ c) ≢ 0 ⟹ \text{\Call{isDead$_U$}{$u'$}}
            \end{aligned}\)
        }
        \EndIf
        \EndFunction
    \end{algorithmic}
\end{algorithm*}

>>>>

\begin{algorithm*}
    \caption{On-the-fly bisimulation algorithm}\label{alg:bisim}
    \begin{algorithmic}
        \Function{equiv}{$s ∈ S, u ∈ U$}
        \If {\Call{eq}{$s, u$}} {\Return true} \EndIf
        \If {\Call{knownDead\(_S\)}{$s$}} 
            \State\Return \Call{isDead\(_U\)}{$u$}
        \EndIf
        \If {\Call{knownDead\(_U\)}{$u$}} 
            \State\Return \Call{isDead\(_S\)}{$s$}
        \EndIf
        \State\Return \(∀ α ∈ \At\) \Comment{conditions in~\Cref{thm:recursive-construction}}
        \\\vspace{5px}
        \(\qquad\begin{aligned}
            & s \transAcc{S}{α} \text{ iff } u \transAcc{U}{α} \mathrel{\&\!\&}\\  
            & s \transRej{S}{α} \text{ and } u \transvia{α ∣ p}_U u' \text{ implies } \Call{isDead\(_U\)}{u'} \mathrel{\&\!\&}\\  
            & s \transvia{α ∣ p}_S s' \text{ and } u \transRej{U}{α} \text{ implies } \Call{isDead\(_U\)}{s'} \mathrel{\&\!\&}\\  
            & s \transvia{α ∣ p}_S s' \text{ and } u \transvia{α ∣ p}_U u' \text{ implies } \Call{union}{s, u}; \Call{equiv}{s', u'} \mathrel{\&\!\&}\\
            & s \transvia{α ∣ p}_S s' \text{ and } u \transvia{α ∣ q}_U u' \text{ and } p ≠ q \text{ implies } \Call{isDead\(_S\)}{s'} \text{ and } \Call{isDead\(_U\)}{u'}
        \end{aligned}\)
        % \Forall{\(α ∈ \At\)}{}{
        %     \Match{$δ_{S}(s, α), δ_{U}(u, α)$}
        %     \Case{\(\accept, \accept\)} {\Continue} \EndCase
        %     \Case{\(\reject, \reject\)} {\Continue} \EndCase
        %     \Case{\(\reject, (u', q)\)} 
        %         \State\Return \Call{isDead\(_U\)}{$u'$} 
        %     \EndCase
        %     \Case{\((s', p), \reject\)}
        %         \State\Return\Call{isDead\(_S\)}{$s'$}
        %     \EndCase
        %     \Case{\((s', p), (u', q)\)} {
        %         \If {\(p = q\)}
        %             \State\Call{union}{$s, u$}
        %             \State\Return \Call{equiv}{$s, t$} 
        %         \EndIf
        %         \If{\Call{isDead\(_S\)}{$s$} and \Call{isDead\(_U\)}{$u$}}
        %             \State\Continue
        %         \EndIf
        %         \State\Return false
        %     } \EndCase
        %     \Default { \Return false } \EndDefault
        %     \EndMatch
        % }\EndFor
        % \State\Return true
        \EndFunction
    \end{algorithmic}
\end{algorithm*}

@@

\begin{algorithm*}
    \caption{Symbolic On-the-fly Bisimulation Algorithm}\label{alg:symb-bisim}
    \begin{algorithmic}
        \Function{equiv}{$s ∈ S, u ∈ U$}
        \If {\Call{eq}{$s, u$}} {\Return true}
        \ElsIf {\Call{knownDead\(_S\)}{$s$}} {\Return \Call{isDead\(_U\)}{$u$}} 
        \ElsIf {\Call{knownDead\(_U\)}{$u$}} {\Return \Call{isDead\(_S\)}{$s$}} 
        \Else {}
        \Return {
            \Comment{conditions of ~\Cref{thm:symb-recursive-construction}}
            \\\vspace{5px}
            \(\qquad
            \begin{aligned}
                & ⋁ ϵ̂_S(s) ≡ ⋁ ϵ̂_U(u) \mathrel{\&\!\&} \\  
                & s \transvia{b ∣ p} s' \text{ and } (b ∧ ρ̂_U(u)) ≢ 0 \text{ implies \Call{isDead$_S$}{$s'$}} \mathrel{\&\!\&}\\
                & u \transvia{b ∣ p} u' \text{ and } (ρ̂_S(s) ∧ b) ≢ 0 \text{ implies \Call{isDead$_U$}{$u'$}} \mathrel{\&\!\&}\\
                & s \transvia{b ∣ p} s' \text{ and } u \transvia{c ∣ p} u' \text{ implies } \text{\Call{Union}{$s$, $u$}}; \text{\Call{Equiv}{$s', u'$}} \mathrel{\&\!\&}\\
                & s \transvia{b ∣ p} s' \text{ and } u \transvia{c ∣ q} u' \text{ and } p ≠ q \text{ implies \Call{isDead}{$s'$} and \Call{isDead}{$u'$}}
            \end{aligned}\)
        }
        \EndIf
        \EndFunction
    \end{algorithmic}
\end{algorithm*}
